---
title: "ELGAN Tractometry Multiverse"
author: "Meaghan Perdue"
date: "9/21/2026"
output: html_document
---
# Tractometry multiverse analysis ELGAN3
This code performs tractmetry analysis on harmonized ELGAN3 pyAFQ data. Picks up following harmonization of ELGAN tractometry data across sites and calculation of PCA factor scores for NIH Toolbox Cognition Battery

## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Read data 
Read harmonized data in AFQ-insight structure (subject-level plus node-level)

```{r}
# Set home directory
base_path<-"/Volumes/LaCie/Projects/elgan_dti/data"

# Read and add to subjects-level data
## Read harmonized pyAFQ subs data
subs<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_subjects.csv"))


## pull in sublist for ID matching and add to subs
sublist<-read.csv(file.path(base_path, "demog_beh", "afq_include.csv")) %>%
  select("subjectID", "sid")

subs<-left_join(subs, sublist, by = "subjectID")

## Read IQ and health data, add to subs
demog<-read.csv(file.path(base_path, "demog_beh", "mergedcorrecteddata_cleaned_MP.csv")) %>%
  select("sid", "ivhx", "plurality", "multip", "dx120_4_asd",	"dx120_5_cp", "epil", "single",	"medu1",	"ins3",	"ins4",	"supp47")

demog2<-read.csv(file.path(base_path, "demog_beh", "elgan_demog_data.csv")) %>%
  select("sid", "develop", "FSIQ2", "srs15")

tmp<-left_join(demog, demog2, by = "sid")

subs<-left_join(subs, tmp, by="sid")

## Read NTCB factor scores and add to subs
#ntcb<-read.csv(file.path(base_path, "demog_beh", "nih_toolbox_factor_scores.csv"))


#subs<-left_join(subs, ntcb, by="subjectID")

## Read MRI Radiology Reports and add 'abnormal' indicator to subs
mri<-read.csv(file.path(base_path, "demog_beh", "MRI083126_summaryVar.csv")) %>%
      select("sid", "mri_abnorm_any")

subs<-left_join(subs, mri, by="sid")

## Create family ID variable (famID) as a derivative of subject ID
subs$famID <- as.factor(substr(as.character(subs$sid), 1, 6))

## write aggregated subject-level data for use in all analyses:

write.csv(subs, file.path(base_path, "demog_beh", "elgan_subject_level_data_for_tractometry.csv"), row.names = FALSE)

# Read harmonized node-level data
nodesprob<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_nodes.csv"))

#Merge subject-level data with nodes
prob<-left_join(nodesprob, subs, by="subjectID")



```

## Nodewise Regression
Run nodewise regression controlling for family-wise error with Threshold-Free Cluster Enhancement
Code developed with Claude Sonnet 5
Update data, tracts, formula, and var_of_interest before running
```{r nodewise regression FSIQ}
source("/Volumes/LaCie/Projects/elgan_dti/code/statistical_analysis/tfce_tractometry.R")

# Setup run per dataset and variable of interest
out <- run_tfce_pipeline_multi_tract(
  data           = prob,   # one row per subject per node per tract
  tracts         = c("CST_L"),  # any tract names in your tract_col
  fixed_formula  = "fa ~ FSIQ2 + mri_age + gadays + bw + female",
  var_of_interest = "FSIQ2",
  tract_col      = "tractID",       # column name identifying tract per row
  subject_col    = "subjectID",
  family_col     = "FamilyID",
  n_permutations = 1000,            # bump up for the real analysis
  random_state   = 1,
  verbose        = FALSE
)

# View summary and plot results per tract
out$summary              # one row per tract: n_significant_nodes, min_pvalue, n_na_nodes_observed
out$results[["CST_L"]]   # full node-level detail for one tract
plot_tfce_result(out$results[["CST_L"]], tract_name = "CST_L")

```


