---
title: "ELGAN Tractometry Multiverse"
author: "Meaghan Perdue"
date: "9/21/2026"
output: html_document
---
# Tractometry multiverse analysis ELGAN3
This code performs tractometry analysis on harmonized ELGAN3 pyAFQ data. Picks up following harmonization of ELGAN tractometry data across sites and calculation of PCA factor scores for NIH Toolbox Cognition Battery

## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Read data 
Read harmonized data in AFQ-insight structure (subject-level plus node-level)

```{r}
# Set home directory
base_path<-"/Volumes/LaCie/Projects/elgan_dti/data"

# Read and add to subjects-level data
## Read harmonized pyAFQ subs data
subs<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_subjects.csv"))


## pull in sublist for ID matching and add to subs
sublist<-read.csv(file.path(base_path, "demog_beh", "afq_include.csv")) %>%
  select("subjectID", "sid")

subs<-left_join(subs, sublist, by = "subjectID")

## Read IQ and health data, add to subs
demog<-read.csv(file.path(base_path, "demog_beh", "mergedcorrecteddata_cleaned_MP.csv")) %>%
  select("sid", "ivhx", "plurality", "multip", "dx120_4_asd",	"dx120_5_cp", "epil", "single",	"medu1",	"ins3",	"ins4",	"supp47")

demog2<-read.csv(file.path(base_path, "demog_beh", "elgan_demog_data.csv")) %>%
  select("sid", "develop", "FSIQ2", "srs15")

tmp<-left_join(demog, demog2, by = "sid")

subs<-left_join(subs, tmp, by="sid")

## Read NTCB factor scores and add to subs
#ntcb<-read.csv(file.path(base_path, "demog_beh", "nih_toolbox_factor_scores.csv"))


#subs<-left_join(subs, ntcb, by="subjectID")

## Read MRI Radiology Reports and add 'abnormal' indicator to subs
mri<-read.csv(file.path(base_path, "demog_beh", "MRI083126_summaryVar.csv")) %>%
      select("sid", "mri_abnorm_any")

subs<-left_join(subs, mri, by="sid")

## Create family ID variable (famID) as a derivative of subject ID
subs$familyID <- as.factor(substr(as.character(subs$sid), 1, 6))

## write aggregated subject-level data for use in all analyses:

write.csv(subs, file.path(base_path, "demog_beh", "elgan_subject_level_data_for_tractometry.csv"), row.names = FALSE)

# Read harmonized node-level data
nodesprob<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_nodes.csv"))

#Merge subject-level data with nodes
prob<-left_join(nodesprob, subs, by="subjectID")

# Filter data to complete cases
model_vars <- c("FSIQ2", "mri_age", "gadays", "bw", "female", "subjectID", "familyID")

prob_complete <- prob %>%
  filter(complete.cases(select(., all_of(model_vars))))

```

## Check correlations among covariates before running tractometry
```{r}
library(psych)
# filter sub-level data to those with FSIQ (n=170)
subs_fsiq<- subs %>%
              filter(complete.cases(select(., all_of(model_vars))))

# summarize data
describe(subs_fsiq)

# select variables for correlation check
subs_fsiq_corr<-subs_fsiq %>%
                    select("FSIQ2", "mri_age", "gadays", "bw")

cor(subs_fsiq_corr)
cor.test(subs_fsiq_corr$gadays, subs_fsiq_corr$bw)


```

## Nodewise Regression
Run nodewise regression controlling for family-wise error with Threshold-Free Cluster Enhancement
Code developed with Claude Sonnet 5
Update data, tracts, formula, and var_of_interest before running
```{r nodewise regression FSIQ}
source("/Volumes/LaCie/Projects/elgan_dti/code/statistical_analysis/tfce_tractometry.R")

tracts<- c("Callosum Anterior Frontal",
           "Callosum Motor",
           "Callosum Occipital", 
           "Callosum Orbital",
           "Callosum Posterior Parietal",
           "Callosum Superior Frontal",      
           "Callosum Superior Parietal", 
           "Callosum Temporal",
           "Left Anterior Thalamic", 
           "Left Arcuate",
           "Left Cingulum Cingulate",
           "Left Corticospinal",
           "Left Inferior Fronto-occipital",  
           "Left Inferior Longitudinal",
           "Left Superior Longitudinal",     
           "Right Anterior Thalamic", 
           "Right Arcuate",      
           "Right Cingulum Cingulate",
           "Right Corticospinal",             
           "Right Inferior Fronto-occipital",
           "Right Inferior Longitudinal",     
           "Right Superior Longitudinal"
           )

# Setup run per dataset and variable of interest
out <- run_tfce_pipeline_multi_tract(
  data           = prob_complete,   # one row per subject per node per tract
  tracts         = c("Right Inferior Longitudinal"),  # any tract names in your tract_col
  fixed_formula  = "dti_fa ~ FSIQ2 + mri_age + gadays + bw + mean_fd + female",
  var_of_interest = "FSIQ2",
  tract_col      = "tractID",       # column name identifying tract per row
  subject_col    = "subjectID",
  family_col     = "familyID",
  n_permutations = 5000,            # bump up for the real analysis
  random_state   = 1,
  verbose        = FALSE
)

# View summary and plot results per tract
out$summary              # one row per tract: n_significant_nodes, min_pvalue, n_na_nodes_observed
out$results[["Right Inferior Longitudinal"]]   # full node-level detail for one tract
plot_tfce_result(out$results[["Right Inferior Longitudinal"]], tract_name = "Callosum Anterior Frontal")

```

## GAMMs
Run GAMMs with continuous variable of interest
```{r GAMMs}
library(mgcv)

# Filter database by tract
prob_complete_RILF<-prob_complete %>%
                      filter(tractID=="Right Inferior Longitudinal")


model <- gam(
  fa ~ s(nodeID, by = FSIQ2) +
       s(nodeID) +
       mri_age + gadays + bw + mean_fd + female + 
       s(subjectID, bs = "re") +
       s(FamilyID, bs = "re"),  
  data = prob_complete_RILF,
  method = "REML"
)

summary(model)
```
