---
title: "ELGAN Tractometry Multiverse"
author: "Meaghan Perdue"
date: "9/21/2026"
output: html_document
---
# Tractometry multiverse analysis ELGAN3
This code performs tractmetry analysis on harmonized ELGAN3 pyAFQ data. Picks up following harmonization of ELGAN tractometry data across sites and calculation of PCA factor scores for NIH Toolbox Cognition Battery

## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Read data
Read harmonized data in AFQ-insight structure (subject-level plus node-level)


```{r}
# Set home directory
base_path<-"/Volumes/LaCie/Projects/elgan_dti/data"

# Read harmonized pyAFQ data
subs<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_subjects.csv"))
nodes<-read.csv(file.path(base_path, "harmonized", "afq_prob", "harmonized_nodes.csv"))

# pull in sublist for ID matching and add to subs
sublist<-read.csv(file.path(base_path, "demog_beh", "afq_include.csv")) %>%
  select("subjectID", "sid")

subs<-left_join(subs, sublist, by = "subjectID")

# Read IQ and health data, add to subs
demog<-read.csv(file.path(base_path, "demog_beh", "mergedcorrecteddata_cleaned_MP.csv")) %>%
  select("sid", "ivhx", "plurality", "multip", "dx120_4_asd",	"dx120_5_cp", "epil", "iq85")

subs<-left_join(subs, demog, by="sid")

# Read NTCB factor scores and add to subs
ntcb<-read.csv(file.path(base_path, "demog_beh", "nih_toolbox_factor_scores.csv"))
  colnames(ntcb)[1]<-"subjectID"

subs<-left_join(subs, ntcb, by="subjectID")

# Read MRI Radiology Reports and add 'abnormal' indicator to subs
mri<-read.csv(file.path(base_path, "demog_beh", "MRI083126_summaryVar.csv") %>%
      select("sid", "mri_abnorm_any")

subs<-left_join(subs, mri, by="sid")




```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
