---
title: "Tractable Test"
output: html_notebook
---

Tractable GAMs on pyAFQ tractometry outputs with Elgan3 UMMS data

## Compile and summarize demographic data
Databases compiled here are used as input for harmonization via AFQ-Insight. 
See harmonize_elgansites.py
```{r demographics}
library(tidyverse)
library(psych)

base_path<-"/Volumes/LaCie/Projects/elgan_dti/data"

sublist<-read.csv(file.path(base_path, "demog_beh", "afq_include.csv"))
# use mri_age from here based on gathering data from elgan_demog_data.csv and Age at Date of MRI

demog<-read.csv(file.path(base_path, "demog_beh", "mergedcorrecteddata_cleaned_MP.csv")) %>%
  select("sid", "bw", "sex", "female", "ivhx", "gadays", "plurality", "multip", "dx120_4_asd",	"dx120_5_cp", "epil", "iq85")

demog2<-read.csv(file.path(base_path, "demog_beh", "elgan_demog_data.csv")) %>%
  select("sid", "develop", "FSIQ2", "srs15")

tmp<-left_join(sublist, demog, by="sid")

subinfo<-left_join(tmp, demog2, by="sid")

# combine diagnosis variables based on McNaughton paper method: ASD, CP, Epilepsy, or IQ<85

subinfo <- subinfo |>
  mutate(ndd = as.integer(
    (dx120_4_asd > 0 & !is.na(dx120_4_asd)) | 
    (dx120_5_cp  > 0 & !is.na(dx120_5_cp))  | 
    (epil        > 0 & !is.na(epil)) |
    (iq85        > 0 & !is.na(iq85))  
  ))

subinfo <- subinfo |>
  mutate(lowiq = as.integer(
    (FSIQ2 <70 & !is.na(FSIQ2)) 
  ))


## create median split variables

# Calculate the median of 'ga_days', excluding NAs
median_bw <- median(subinfo$bw, na.rm = TRUE)

# Create the 'bw_group' column
subinfo$bw_group <- ifelse(is.na(subinfo$bw), NA, ifelse(subinfo$bw > median_bw, "High", "Low"))

# Optionally convert to factor
subinfo$bw_group <- factor(subinfo$bw_group, levels = c("Low", "High"))

# Calculate the median of 'ga_days', excluding NAs
median_ga <- median(subinfo$gadays, na.rm = TRUE)

# Create the 'ga_group' column
subinfo$ga_group <- ifelse(subinfo$gadays > median_ga, "High", "Low")


# read in QSIprep QC data and select relevant columns
qc<-read.csv(file.path(base_path, "qsiprep_qc_combined.csv")) %>%
  mutate(
    subjectID = str_remove(subjectID, "^sub-"),
    sessionID = str_remove(sessionID, "^ses-")
  )

# add QC data to subinfo
subinfo<-left_join(subinfo, qc, by = "subjectID")

# Filter out participants with mean framewise displacement >1mm
subinfo_filtered<-subinfo %>%
                    filter(mean_fd<=1)

write.csv(subinfo_filtered, "/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_tractometry_subinfo_filtered.csv", row.names=FALSE)

```


#Describe Data Participant Characteristics 
```{r}
## describe data

subinfo_filtered %>% count(female)
subinfo_filtered %>% count(ndd)
subinfo_filtered %>% count(ivhx)
subinfo_filtered %>% count(iq85) # coded from mergedandcorrected data sheet

describe(subinfo_filtered)



# describe subset with IQ data
subinfo_IQsubset <- subinfo_filtered %>% 
                        filter(!is.na(iq85))

subinfo_IQsubset %>% count(female)
subinfo_IQsubset %>% count(ndd)
subinfo_IQsubset %>% count(ivhx)
subinfo_IQsubset %>% count(iq85) # coded from mergedandcorrected data sheet

describe(subinfo_IQsubset)

```

# Load data - AFQ waypoints tracts

```{r}

library(tidyverse)

# Define base path and site IDs
base_path <- "/Volumes/LaCie/Projects/elgan_dti/data"
sites <- c("site-120", "site-130", "site-140", "site-150", "site-160",
           "site-170", "site-220", "site-230", "site-310", "site-320", "site-330")

# Build file paths
tract_profile_paths <- file.path(base_path, sites, "derivatives", "afq", "tract_profiles.csv")

# Name the vector so site labels are preserved
names(tract_profile_paths) <- sites

# Vendor lookup
vendor_map <- c(
  "site-120" = "Siemens",
  "site-130" = "Siemens",
  "site-140" = "Siemens",      
  "site-150" = "Philips",
  "site-160" = "Philips",
  "site-170" = "Siemens",
  "site-220" = "Siemens",
  "site-230" = "Siemens",
  "site-310" = "GE",
  "site-320" = "GE",
  "site-330" = "Philips"
)

# Read and combine, adding 'site' and 'vendor' columns
tract_profiles_combined <- tract_profile_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site") |>
  mutate(vendor = vendor_map[site]) |>
  type_convert()

# Preview
glimpse(tract_profiles_combined)

# Add demographic data to tract profiles
elgan_afq_prob<-inner_join(tract_profiles_combined, subinfo_filtered, by = "subjectID")

write.csv(elgan_afq_prob, "/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_filtered.csv", row.names=FALSE)


# Load database for analysis
elgan_afq_prob <- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_filtered.csv") 

elgan_afq_prob <- elgan_afq_prob %>%
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))


```

## Load Deterministic AFQ data and compile
```{r}
# Define base path and site IDs
base_path <- "/Volumes/LaCie/Projects/elgan_dti/data"
sites <- c("site-120", "site-130", "site-140", "site-150", "site-160",
           "site-170", "site-220", "site-230", "site-310", "site-320", "site-330")

# Build file paths
tract_profile_paths <- file.path(base_path, sites, "derivatives", "afq_det", "tract_profiles.csv")

# Name the vector so site labels are preserved
names(tract_profile_paths) <- sites

# Vendor lookup
vendor_map <- c(
  "site-120" = "Siemens",
  "site-130" = "Siemens",
  "site-140" = "Siemens",      
  "site-150" = "Philips",
  "site-160" = "Philips",
  "site-170" = "Siemens",
  "site-220" = "Siemens",
  "site-230" = "Siemens",
  "site-310" = "GE",
  "site-320" = "GE",
  "site-330" = "Philips"
)

# Read and combine, adding 'site' and 'vendor' columns
det_tract_profiles_combined <- tract_profile_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site") |>
  mutate(vendor = vendor_map[site]) |>
  type_convert()


# Add demographic data to tract profiles
elgan_afq_det<-inner_join(det_tract_profiles_combined, subinfo_filtered, by = "subjectID")

write.csv(elgan_afq_det, "/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_det_filtered.csv", row.names=FALSE)


# Load database for analysis
#elgan_afq_det <- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_det_filtered.csv") 

elgan_afq_det <- elgan_afq_det %>%
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))
```

## Load AFQ Probabilistic Ends-Clipped and compile
```{r}
# Define base path and site IDs
base_path <- "/Volumes/LaCie/Projects/elgan_dti/data"
sites <- c("site-120", "site-130", "site-140", "site-150", "site-160",
           "site-170", "site-220", "site-230", "site-310", "site-320", "site-330")

# Build file paths
tract_profile_paths <- file.path(base_path, sites, "derivatives", "afq_prob_clip", "tract_profiles.csv")

# Name the vector so site labels are preserved
names(tract_profile_paths) <- sites

# Vendor lookup
vendor_map <- c(
  "site-120" = "Siemens",
  "site-130" = "Siemens",
  "site-140" = "Siemens",      
  "site-150" = "Philips",
  "site-160" = "Philips",
  "site-170" = "Siemens",
  "site-220" = "Siemens",
  "site-230" = "Siemens",
  "site-310" = "GE",
  "site-320" = "GE",
  "site-330" = "Philips"
)

# Read and combine, adding 'site' and 'vendor' columns
prob_clip_tract_profiles_combined <- tract_profile_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site") |>
  mutate(vendor = vendor_map[site]) |>
  type_convert()


# Add demographic data to tract profiles
elgan_afq_prob_clip<-inner_join(prob_clip_tract_profiles_combined, subinfo_filtered, by = "subjectID")

write.csv(elgan_afq_prob_clip, "/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_clip_filtered.csv", row.names=FALSE)


# Load database for analysis
#elgan_afq_prob_clip <- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_clip_filtered.csv") 

elgan_afq_prob_clip <- elgan_afq_prob_clip %>%
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))
```

## Load deterministic-clipped ends and compile
```{r}
# Define base path and site IDs
base_path <- "/Volumes/LaCie/Projects/elgan_dti/data"
sites <- c("site-120", "site-130", "site-140", "site-150", "site-160",
           "site-170", "site-220", "site-230", "site-310", "site-320", "site-330")

# Build file paths
tract_profile_paths <- file.path(base_path, sites, "derivatives", "afq_det_clip", "tract_profiles.csv")

# Name the vector so site labels are preserved
names(tract_profile_paths) <- sites

# Vendor lookup
vendor_map <- c(
  "site-120" = "Siemens",
  "site-130" = "Siemens",
  "site-140" = "Siemens",      
  "site-150" = "Philips",
  "site-160" = "Philips",
  "site-170" = "Siemens",
  "site-220" = "Siemens",
  "site-230" = "Siemens",
  "site-310" = "GE",
  "site-320" = "GE",
  "site-330" = "Philips"
)

# Read and combine, adding 'site' and 'vendor' columns
det_clip_tract_profiles_combined <- tract_profile_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site") |>
  mutate(vendor = vendor_map[site]) |>
  type_convert()


# Add demographic data to tract profiles
elgan_afq_det_clip<-inner_join(det_clip_tract_profiles_combined, subinfo_filtered, by = "subjectID")

write.csv(elgan_afq_det_clip, "/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_det_clip_filtered.csv", row.names=FALSE)


# Load database for analysis
#elgan_afq_det_clip <- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_det_clip_filtered.csv") 

elgan_afq_det_clip <- elgan_afq_det_clip %>%
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))
```

## Check out QC differences by vendor, site, and analysis groups of interest

```{r}
## reduce dataframe to relevant columns with 1 row per subject
df_qc<- elgan_afq_prob %>% 
          select("subjectID", "vendor", "site", "female","iq85", "ga_group", "bw_group", 31:89) %>%
          distinct()

write.csv(df_qc, "/Volumes/LaCie/Projects/elgan_dti/data/qsiprep_qc_combined_vendor_site.csv", row.names=FALSE)
      
# Run ANOVA by Vendor

summary(aov(CNR1_mean ~ vendor, dat=df_qc))

ggplot(data=df_qc) +
  geom_violin(aes(x=vendor, y=CNR1_mean))

## post-hoc pairwise tests
TukeyHSD(aov(CNR1_mean ~ vendor, data=df_qc))

summary(aov(mean_fd ~ vendor, data=df_qc))

summary(aov(mean_fd ~ vendor, data=df_qc))

# Run ANOVA by Site
summary(aov(CNR0_mean ~ site, data=df_qc))



## Mean Framewise Displacement
summary(aov(mean_fd ~ vendor, dat=df_qc))

ggplot(data=df_qc) + 
  geom_boxplot(aes(x=vendor, y=mean_fd)) +
  theme_classic()

summary(aov(mean_fd ~ site, dat=df_qc))

ggplot(data=df_qc) +
  geom_boxplot(aes(x=site, y=mean_fd)) +
  theme_classic()

## Raw number bad slices
summary(aov(raw_num_bad_slices ~ vendor, dat=df_qc))

ggplot(data=df_qc) + 
  geom_boxplot(aes(x=vendor, y=raw_num_bad_slices)) +
  theme_classic()

summary(aov(raw_num_bad_slices ~ site, dat=df_qc))

ggplot(data=df_qc) +
  geom_boxplot(aes(x=site, y=raw_num_bad_slices)) +
  theme_classic()

## QC differences by IQ group
t.test(mean_fd ~ iq85, dat=df_qc) ## NOT SIG

t.test(mean_fd ~ ga_group, dat=df_qc)
t.test(mean_fd ~ bw_group, dat=df_qc) ## p=.0495


```


