#' 1D Threshold-Free Cluster Enhancement (TFCE) for tractometry node profiles

Implements TFCE (Smith & Nichols, 2009) adapted to a 1D array of along-tract
nodes (e.g., 100 pyAFQ/AFQ-Insight nodes per tract), combined with a
restricted (family-block) permutation test for family-wise error control
across nodes -- avoiding both the arbitrary single-threshold problem AND
respecting sibling/family clustering assumed by a `(1 | FamilyID)` random
effect in the node-wise model.

Typical workflow:
  1. Fit your node-wise mixed model (e.g., fa ~ IQ + AgeMRI + GestationalAge
      + Sex + (1 | FamilyID)) once per node on the real data to get an
      observed statistic profile (t-values for IQ), via `nodewise_lmer()`.
   2. Convert that profile to a TFCE score profile with `tfce_1d()`.
   3. Repeat 1-2 many times with IQ permuted via family-block restricted
      permutation (`family_block_permutation()`), recording max |TFCE|
      each time (`permutation_test_tfce()`).
   4. Use the null distribution of max |TFCE| to assign a corrected
      p-value to every node's observed TFCE score.

  Run separately per tract (one contiguous chain of 100 nodes).

## Load libraries
```{r}
library(lme4)
library(dplyr)
```

## 1. Core TFCE computation on a 1D stat profile

```{r}
#' TFCE contribution from the positive tail of `stat` only.
#' NA entries (missing nodes) break cluster contiguity rather than counting
#' as zero.
.tfce_one_sign <- function(stat, E, H, n_steps) {
  n <- length(stat)
  tfce <- numeric(n)

  valid <- !is.na(stat)
  if (!any(valid)) return(tfce)

  pos_vals <- stat[valid]
  max_stat <- if (any(pos_vals > 0)) max(pos_vals) else 0
  if (max_stat <= 0) return(tfce)

  thresholds <- seq(max_stat / n_steps, max_stat, length.out = n_steps)
  dh <- if (n_steps > 1) thresholds[2] - thresholds[1] else max_stat

  for (h in thresholds) {
    supra <- ifelse(valid, stat >= h, FALSE)
    if (!any(supra)) next

    # find contiguous runs of TRUE in `supra`
    padded <- c(FALSE, supra, FALSE)
    diffs <- diff(as.integer(padded))
    starts <- which(diffs == 1)       # 1-indexed start of run (in padded coords)
    ends <- which(diffs == -1) - 1    # 1-indexed end of run (in padded coords)
    # padded coords are shifted by +1 relative to `stat`, so index n in
    # `stat` corresponds to index n+1 in `padded` -- starts/ends above are
    # already in `stat`-index terms after the -0 / -1 adjustment: starts
    # (from padded, 1-indexed) map directly to stat 1-indexed start; ends
    # computed as (which(diffs==-1) - 1) map directly to stat 1-indexed end.

    for (i in seq_along(starts)) {
      s <- starts[i]
      e <- ends[i]
      extent <- e - s + 1
      contribution <- (extent ^ E) * (h ^ H) * dh
      tfce[s:e] <- tfce[s:e] + contribution
    }
  }

  tfce
}

#' Compute the signed 1D TFCE score at every node from a node-wise statistic
#' profile (e.g., t-values from a node-wise regression).
#'
#' @param stat Numeric vector of length n_nodes. Node-wise test statistic
#'   (t-value, z-value, etc). Sign matters -- positive and negative effects
#'   are enhanced separately. Use NA for missing/invalid nodes; these break
#'   cluster contiguity rather than being treated as stat = 0.
#' @param E,H TFCE extent and height exponents. E=0.5, H=2.0 are the FSL /
#'   Smith & Nichols (2009) defaults, used here as a reasonable default --
#'   there is no tractometry-specific validated setting, so treat these as
#'   adjustable and consider a sensitivity check across a couple of (E, H)
#'   pairs alongside a cluster/threshold sensitivity check.
#' @param n_steps Number of threshold steps for the numerical integral over
#'   height. 100 is fine-grained enough for a ~100-node profile.
#' @param two_sided If TRUE (default), compute TFCE separately for the
#'   positive and negative tails and return their difference (positive minus
#'   negative), preserving sign. If FALSE, only the positive tail is enhanced.
#' @return Numeric vector of length n_nodes, signed TFCE-enhanced scores.
#'   Nodes that were NA in `stat` remain NA.
tfce_1d <- function(stat, E = 0.5, H = 2.0, n_steps = 100, two_sided = TRUE) {
  stat <- as.numeric(stat)
  pos_tfce <- .tfce_one_sign(stat, E, H, n_steps)

  if (two_sided) {
    neg_tfce <- .tfce_one_sign(-stat, E, H, n_steps)
    tfce <- pos_tfce - neg_tfce
  } else {
    tfce <- pos_tfce
  }

  tfce[is.na(stat)] <- NA
  tfce
}
```


## 2. Node-wise mixed-effects regression, run once per node across a tract

```{r}
#' Fit a random-intercept mixed model independently at every node of a
#' single tract, and return the node-wise t-value for `var_of_interest`.
#'
#' This is the R/lme4 equivalent of a per-node LMER such as:
#'   fa ~ IQ + AgeMRI + GestationalAge + Sex + (1 | FamilyID)
#' fit separately at each of the 100 nodes.
#'
#' @param df Long-format data for ONE tract: one row per subject per node.
#'   Must contain `node_col`, `group_col`, and all variables in `fixed_formula`.
#' @param fixed_formula A formula string for the FIXED effects only, e.g.
#'   "fa ~ IQ + AgeMRI + GestationalAge + Sex" -- the random-effect term is
#'   added automatically from `group_col`.
#' @param var_of_interest Name of the fixed-effect coefficient (as lme4 will
#'   report it -- check `names(fixef(fit))` once if unsure, e.g. for a
#'   factor term) whose node-wise t-value you want back.
#' @param group_col Column defining the random-intercept grouping variable
#'   (e.g. "FamilyID").
#' @param node_col Column identifying node position (0..n_nodes-1, or
#'   1..n_nodes -- just be consistent with `n_nodes` and the node values
#'   actually present in `df`).
#' @param n_nodes Total number of nodes in the tract (100 for standard
#'   pyAFQ/AFQ-Insight output).
#' @param min_rows Minimum rows required at a node to attempt a fit.
#' @return Numeric vector of length n_nodes; NA at nodes with insufficient
#'   data or a convergence/singularity failure.

nodewise_lmer <- function(df, fixed_formula, var_of_interest, group_col,
                           node_col = "nodeID", n_nodes = 100, min_rows = 10) {
  stat_profile <- rep(NA_real_, n_nodes)
  full_formula <- as.formula(
    paste(fixed_formula, "+ (1 |", group_col, ")")
  )
  node_values <- sort(unique(df[[node_col]]))

  for (node in node_values) {
    node_df <- df[df[[node_col]] == node, ]
    if (nrow(node_df) < min_rows) next

    fit <- tryCatch({
      # suppress the routine singular-fit / convergence messages here;
      # they're summarized separately after the full permutation run
      # rather than printed per node per permutation
      suppressMessages(suppressWarnings(
        lmer(full_formula, data = node_df, REML = TRUE,
             control = lmerControl(check.conv.singular = "ignore"))
      ))
    }, error = function(e) NULL)

    if (is.null(fit)) next

    coefs <- summary(fit)$coefficients
    if (!(var_of_interest %in% rownames(coefs))) next

    # index 1..n_nodes assuming node_values are 0-indexed contiguous or
    # 1-indexed contiguous; store by position to stay robust to either
    idx <- match(node, node_values)
    stat_profile[idx] <- coefs[var_of_interest, "t value"]
  }

  stat_profile
}
```
