---
title: "ntcb Factor Score Calculation ELGAN3"
output: html_notebook
---

Calculate factor scores for Verbal Cognition and Fluid Cognition factors from Joseph et al. 2022 PCA
Recalculating factors from loadings matrix and NIH toolbox raw scores for DTI subset
Scripting help from Claude Sonnet5

```{r - load data}
library(tidyverse)

#load raw ntcb data and filter out empty rows, add subject id column
raw<- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/demog_beh/nih_toolbox_dti_subset.csv") %>%
  filter(
    if_any(
      -studyid,
      ~ coalesce(trimws(as.character(.)), "") != ""
    )
  ) %>%
  mutate(SubjectID = paste0("E", studyid))

#Select relevant columns for analysis - age-corrected standard scores

ntcb<- raw %>%
          select(SubjectID, studyid, ageCrystalCmp, ageFluidCmp, ageTotalCmp, ends_with("ageStd"))

```

# Run PCA on DTI subset to check if it aligns with Joseph et al. 2022 results
```{r PCA}
library(psych)

# Define the columns of interest
pca_vars <- c("CSageStd", "FLageStd", "LSageStd", "ORageStd", "PCageStd", "PSageStd", "PVageStd")

# Subset the data
pca_data <- ntcb[, pca_vars]

# Check for missing values first — prcomp() will fail or drop rows silently otherwise
sum(!complete.cases(pca_data))

# Drop two incomplete cases
pca_data <- pca_data[complete.cases(pca_data), ]

# Run PCA (center and scale, since these are likely on similar but not identical scales)
pca_rotated <- principal(pca_data, nfactors = 2, rotate = "varimax")
print(pca_rotated, cut = 0.3, sort = TRUE)

# Visualize loadings on first 2 components
biplot(pca_rotated, scale = 0)





```

# Calculate factor scores based on the original Joseph et al 2022 PCA that was done in the full sample \
Factor 1 (Verbal): Picture Vocabulary, Oral Reading, List Sorting WM
Factor 2 (Fluid): Flanker, Dimensional Change Card Sort, Pattern Comparison Processing Speed
```{r - calculate scores}
library(psych)

# ------------------------------------------------------------
# 1. Standardize the indicator variables (z-scores)
# ------------------------------------------------------------
indicator_vars <- c("PVageStd", "ORageStd", "LSageStd", "FLageStd", "CSageStd", "PCageStd")
z_data <- scale(ntcb[, indicator_vars])

# ------------------------------------------------------------
# 2. Compute factor scores using the averaging method
# ------------------------------------------------------------
verbal_vars <- c("PVageStd", "ORageStd", "LSageStd")
fluid_vars  <- c("FLageStd", "CSageStd", "PCageStd")

ntcb <- ntcb %>%
  mutate(
    Verbal_Composite = rowMeans(z_data[, verbal_vars], na.rm = TRUE),
    Fluid_Composite  = rowMeans(z_data[, fluid_vars], na.rm = TRUE)
  )

# ------------------------------------------------------------
# 4. Compute factor scores using the regression method
#    FS = Z %*% R^-1 %*% L
# ------------------------------------------------------------
R <- cor(ntcb[, indicator_vars], use = "complete.obs")
R_inv <- solve(R)

factor_score_weights <- R_inv %*% loadings_matrix
factor_scores <- z_data %*% factor_score_weights

colnames(factor_scores) <- c("VerbalCognition_Score", "FluidCognition_Score")

# ------------------------------------------------------------
# 5. Combine with subject IDs
# ------------------------------------------------------------
results <- cbind(SubjectID = ntcb$SubjectID, as.data.frame(factor_scores))
print(results)

# write.csv(results, "factor_scores.csv", row.names = FALSE)

```

