---
title: "Tractable Test"
output: html_notebook
---

Testing Tractable to run GAMs on pyAFQ tractometry outputs with Elgan3 UMMS data

# Load libraries
```{r setup}
library(tractable)
library(dplyr)
library(ggplot2)
```

# Load data - AFQ waypoints tracts

```{r}
# Read and complile AFQ tract profiles data

site160<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/Site-160_ELGAN/derivatives/afq/tract_profiles.csv")

site150<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/Site-150/derivatives/afq/tract_profiles.csv")

afqtracts<-bind_rows(site160, site150)

# read in subjects list for analysis
subs<-read.table("/Volumes/LaCie/Projects/elgan_dti/data/afq_include.tsv", sep = "\t", header= TRUE)

# read in demographic/behavioral data and filter to included subs
#demos<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/elgan_demog_data.csv") %>%
#          right_join(subs, by = c("sid", "subjectID"))

ses<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ses_variables_steve071525.csv") 

subs<-left_join(subs, ses, by = "sid")

#read in clinical data
clin<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/mergedcorrecteddata_cleaned_MP.csv") %>%
                  select(c("sid", "bw", "gadays", "multip", "asd", "ados", "adhdr", "epili", "ldgroup", "dx120_4_asd", "dx120_5_cp"))


              
subs<-left_join(subs, clin, by = "sid")

# recode ld groups as yes/no variable (ldgroup variable: WIAT LD group Math x Read (MR, R, M, neither: 1,2,3,4))
subs$ld<-ifelse(subs$ldgroup<4, 1, 0)

#add dichotomized variable for SRS (0 or any risk) at each time point
subs$srs2_any <- ifelse(subs$srs2 > 0, 1, 0)
subs$srs10_any <- ifelse(subs$srs10 > 0, 1, 0)
subs$srs15_any <- ifelse(subs$srs15 > 0, 1, 0)

# add cumulative SRS score for risk factors over time points
subs$srs_cumulative <- subs$srs2 + subs$srs10 + subs$srs15
subs$srs_cumulative_high <- ifelse(subs$srs_cumulative > 0, 1, 0)

# add dichotomized FSIQ variable <85=1
subs$fsiq_low <- ifelse(subs$FSIQ2<85,1,0)

# add combined variable for low IQ x LD
subs$ld_lowIQ <- ifelse(subs$fsiq_low==1 & subs$ld==1, 1,0)

# add ld variable for "specific" LD kids withOUT low IQ
subs$sld <- ifelse(subs$fsiq_low==0 & subs$ld==1, 1,0)

# compile all data for analysis
afq<-left_join(subs, afqtracts, by= "subjectID") 

# make variables factors for GAM analysis
afq$sex<-as.factor(afq$sex)
afq$subjectID<-as.factor(afq$subjectID)
afq$earlyi<-as.factor(afq$earlyi)
#afq$srs2_any<-as.factor(afq$srs2_any)
#afq$srs10_any<-as.factor(afq$srs10_any)
#afq$srs15_any<-as.factor(afq$srs15_any)
afq$srs_cumulative_high<-as.factor(afq$srs_cumulative_high)
afq$fsiq_low<-as.factor(afq$fsiq_low)
afq$ld_lowIQ<-as.factor(afq$ld_lowIQ) 
afq$ld<-as.factor(afq$ld)
afq$adhdr<-as.factor(afq$adhdr)

#afq$bw_group<-as.factor(afq$bw_group)
#afq$ga_group<-as.factor(afq$ga_group)

```

# Participants summary
```{r}
library(psych)

subs_iq<-filter(subs, !is.na(subs$FSIQ2))

desc <- as.data.frame(describe(subs_iq, na.rm= TRUE)) %>%
          filter(row.names(as.data.frame(describe(subs_iq, na.rm= TRUE))) %in% c("age_mri", "gadays", "bw", "FSIQ2")) %>%
          select("mean", "sd", "median", "min", "max")


colnames(desc) <- c("Mean", "SD", "Median", "Min.", "Max.")
row.names(desc) <- c("Age at MRI (yrs)", "IQ (SS)", "Birth Weight (g)", "Gestational Age at Birth (days)")
desc          

write.csv(desc, "/Users/meaghan/Library/CloudStorage/OneDrive-UMassChanMedicalSchool/ELGAN/ELGAN_Tractometry/abstracts/ohbm_descriptives.csv")

count(subs_iq, sex, group_by=site)

count(subs_iq, fsiq_low)


summary(elgan$sex)

```

# Plot Profiles - AFQ waypoints tracts
## Plot FA by basic demographic info
```{r plot_profiles_afq}
#check for site differences
plot_fa_by_site <- plot_tract_profiles(
  df = afq,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "site",
  save_figure = FALSE
)
plot_fa_by_site


# sex differences
plot_fa_by_sex <- plot_tract_profiles(
  df = afq,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "sex",
  save_figure = FALSE
)
plot_fa_by_sex

```

## Plot by neurodevelopmental variables
```{r plot by NDDs}

#FSIQ <85
# filter out missing IQ data
afq_iq<-filter(afq, !is.na(afq$fsiq_low))

plot_fa_by_iq <- plot_tract_profiles(
  df = afq_iq,
  y = c("dti_fa"),
  tracts = c("Callosum Orbital", "Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "fsiq_low",
  group_pal = "cbb",
  save_figure = FALSE
plot_fa_by_iq



# Learning Disability (Reading and/or math)
afq_ld<-filter(afq, !is.na(afq$ld))

plot_fa_by_ld <- plot_tract_profiles(
  df = afq_ld,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "ld",
  save_figure = FALSE
)
plot_fa_by_ld


# ADHD
afq_adhd<-filter(afq, !is.na(afq$adhdr))


plot_fa_by_adhd <- plot_tract_profiles(
  df = afq_adhd,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "adhdr",
  save_figure = FALSE
)
plot_fa_by_adhd


```

## Plot FA by SES risk factors
```{r plot by SES variables}
# filter out participant with missing earlyi variable (31/45 subs had early intervention/infant stimulation)
afq_earlyi <- filter(afq, !is.na(earlyi))

plot_fa_by_earlyi <- plot_tract_profiles(
  df = afq_earlyi,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "earlyi",
  save_figure = FALSE
)
plot_fa_by_earlyi

# filter out participant with missing srs2 variable 
afq_srs2 <- filter(afq, !is.na(srs2_any))

plot_fa_by_srs2 <- plot_tract_profiles(
  df = afq_srs2,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "srs2_any",
  save_figure = FALSE
)
plot_fa_by_srs2

# filter out participant with missing srs10 variable 
afq_srs10 <- filter(afq, !is.na(srs10_any))

plot_fa_by_srs10 <- plot_tract_profiles(
  df = afq_srs10,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "srs10_any",
  save_figure = FALSE
)
plot_fa_by_srs10



# filter out participant with missing srs15 variable 
afq_srs15 <- filter(afq, !is.na(srs15_any))

plot_fa_by_srs15 <- plot_tract_profiles(
  df = afq_srs15,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "srs15_any",
  save_figure = FALSE
)
plot_fa_by_srs15

# Plot by cumulative SRS risk (sum of total SRS scores for each time point, split >1)

afq_srs <- filter(afq, !is.na(srs_cumulative))

afq_srs$srs_cumulative_high<-as.factor(afq_srs$srs_cumulative_high)

plot_fa_by_srs_all <- plot_tract_profiles(
  df = afq_srs,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "srs_cumulative_high",
  save_figure = FALSE
)
plot_fa_by_srs_all

```

# Fit GAMs by tract - AFQ Waypoints Tracts
Make sure node group variable and subjectID are set as factors, else an error will occur


## FSIQ
```{r fit FSIQ<85}
########## CC Orbital ###################################
CCorb_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Callosum Orbital",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCorb_iq_summary <- summary(CCorb_iq_fit)
CCorb_iq_summary

############### CC Ant. Frontal. #########################
CCant_iq_fit<-tractable_single_tract(
  df = afq,
  tract = "Callosum Anterior Frontal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCant_iq_summary <- summary(CCant_iq_fit)
CCant_iq_summary

################ CC Sup. Frontal ##########################

CCsupf_iq_fit<-tractable_single_tract(
  df = afq,
  tract = "Callosum Superior Frontal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCsupf_iq_summary <- summary(CCsupf_iq_fit)
CCsupf_iq_summary

################# CC. Motor ##################################

CCmot_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Callosum Motor",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCmot_iq_summary <- summary(CCmot_iq_fit)
CCmot_iq_summary

##### SIG Effect!

################ CC Sup. Parietal #######################

CCsuppar_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Callosum Superior Parietal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCsuppar_iq_summary <- summary(CCsuppar_iq_fit)
CCsuppar_iq_summary

##### SIG but unlikely to survive corrections

############### CC Post. Parietal #########################
CCpostpiq_fit <- tractable_single_tract(
  df = afq,
  tract = "Callosum Posterior Parietal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCpostp_iq_summary <- summary(CCpostpiq_fit)
CCpostp_iq_summary

################ CC Occipital #############################
CCocc_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Callosum Occipital",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

CCocc_iq_summary <- summary(CCocc_iq_fit)
CCocc_iq_summary

############### L. Ant. Thalamic ##########################
LATh_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Anterior Thalamic",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LATh_iq_summary <- summary(LATh_iq_fit)
LATh_iq_summary

############### R. Ant. Thalamic ##########################
RATh_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Anterior Thalamic",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RATh_iq_summary <- summary(RATh_iq_fit)
RATh_iq_summary


################ L. Arcuate ###############################

LAF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Arcuate",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LAF_iq_summary <- summary(LAF_iq_fit)
LAF_iq_summary

############### R. Arcuate #######################################
RAF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Arcuate",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RAF_iq_summary <- summary(RAF_iq_fit)
RAF_iq_summary

############### L. Cingulum ######################################
LCing_iq_fit<- tractable_single_tract(
  df = afq,
  tract = "Left Cingulum Cingulate",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LCing_iq_summary <- summary(LCing_iq_fit)
LCing_iq_summary

################### R. Cingulum ##################################
RCing_iq_fit<- tractable_single_tract(
  df = afq,
  tract = "Right Cingulum Cingulate",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RCing_iq_summary <- summary(RCing_iq_fit)
RCing_iq_summary

##################### L. Corticospinal ############################
LCST_iq_fit<- tractable_single_tract(
  df = afq,
  tract = "Left Corticospinal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LCST_iq_summary <- summary(LCST_iq_fit)
LCST_iq_summary


####################### R. Corticospinal ###########################
RCST_iq_fit<- tractable_single_tract(
  df = afq,
  tract = "Right Corticospinal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RCST_iq_summary <- summary(RCST_iq_fit)
RCST_iq_summary


################ L. IFO ##########################################

LIFO_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LIFO_iq_summary <- summary(LIFO_iq_fit)
LIFO_iq_summary

###### Marginal

############## R. IFO ############################################
LIFO_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LIFO_iq_summary <- summary(LIFO_iq_fit)
LIFO_iq_summary

#################### R. IFO ######################################

RIFO_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RIFO_iq_summary <- summary(RIFO_iq_fit)
RIFO_iq_summary


##### marginal

################# L. ILF #######################################
LILF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Inferior Longitudinal",
  target = "dti_fa",
  regressors = c("site", "sex","fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LILF_iq_summary <- summary(LILF_iq_fit)
LILF_iq_summary

########## sig. but small

################# R. ILF #########################################

RILF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Inferior Longitudinal",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RILF_iq_summary <- summary(RILF_iq_fit)
RILF_iq_summary

####### Significant IQ effect


################## L. SLF ###########################
LSLF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Superior Longitudinal",
  target = "dti_fa",
  regressors = c("site", "sex","fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

LSLF_iq_summary <- summary(LSLF_iq_fit)
LSLF_iq_summary

################## R. SLF ###########################
RSLF_iq_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Superior Longitudinal",
  target = "dti_fa",
  regressors = c("site", "sex","fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

RSLF_iq_summary <- summary(RSLF_iq_fit)
RSLF_iq_summary

```



### FDR correction for FSIQ models
```{r FDR corr}
tracts<-c("CC Anterior Frontal", "CC Motor", "CC Occipital", "CC Orbital", "CC Posterior Parietal", "CC Superior Frontal", "CC Superior Parietal","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Arcuate", "Right Arcuate", "Left Cingulum", "Right Cingulum", "Left Corticospinal", "Right Corticospinal", "Left Inferior Fronto-Occipital", "Right Inferior Fronto-Occipital", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Superior Longitudinal", "Right Superior Longitudinal")

fitcoef<-c(CCant_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LATh_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RATh_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LAF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RAF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LCing_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RCing_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LCST_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RCST_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LILF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RILF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.coeff"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.coeff"]][["fsiq_low1"]])

tvals<-c(CCant_iq_summary[["p.t"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.t"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.t"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.t"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.t"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.t"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.t"]][["fsiq_low1"]],
          LATh_iq_summary[["p.t"]][["fsiq_low1"]],
          RATh_iq_summary[["p.t"]][["fsiq_low1"]],
          LAF_iq_summary[["p.t"]][["fsiq_low1"]],
          RAF_iq_summary[["p.t"]][["fsiq_low1"]],
          LCing_iq_summary[["p.t"]][["fsiq_low1"]],
          RCing_iq_summary[["p.t"]][["fsiq_low1"]],
          LCST_iq_summary[["p.t"]][["fsiq_low1"]],
          RCST_iq_summary[["p.t"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.t"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.t"]][["fsiq_low1"]],
          LILF_iq_summary[["p.t"]][["fsiq_low1"]],
          RILF_iq_summary[["p.t"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.t"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.t"]][["fsiq_low1"]])

pvals<-c( CCant_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.pv"]][["fsiq_low1"]],
          LATh_iq_summary[["p.pv"]][["fsiq_low1"]],
          RATh_iq_summary[["p.pv"]][["fsiq_low1"]],
          LAF_iq_summary[["p.pv"]][["fsiq_low1"]],
          RAF_iq_summary[["p.pv"]][["fsiq_low1"]],
          LCing_iq_summary[["p.pv"]][["fsiq_low1"]],
          RCing_iq_summary[["p.pv"]][["fsiq_low1"]],
          LCST_iq_summary[["p.pv"]][["fsiq_low1"]],
          RCST_iq_summary[["p.pv"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.pv"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.pv"]][["fsiq_low1"]],
          LILF_iq_summary[["p.pv"]][["fsiq_low1"]],
          RILF_iq_summary[["p.pv"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.pv"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.pv"]][["fsiq_low1"]])

pfdr<-p.adjust(pvals, method = "fdr", n=length(pvals))

results_iq<-data_frame(tracts, fitcoef, tvals, pvals, pfdr)

write.csv(results_iq, "/Users/meaghan/Library/CloudStorage/OneDrive-UMassChanMedicalSchool/ELGAN/ELGAN_Tractometry/abstracts/ohbm_results.csv")


```

## Compare Recobundles outputs
Just doing major bundles since most were not accurately segmented
```{r recobundles}
recosite160<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/Site-160_ELGAN/derivatives/afq_recobundles/tract_profiles.csv")

recosite150<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/Site-150/derivatives/afq_recobundles/tract_profiles.csv")

recotracts<-bind_rows(recosite160, recosite150)

reco<-left_join(subs, recotracts, by= "subjectID") 

## Plot recobundles profiles
reco_iq<-filter(reco, !is.na(reco$fsiq_low))

reco_iq$fsiq_low<-as.factor(reco_iq$fsiq_low)
reco_iq$site<-as.factor(reco_iq$site)
reco_iq$sex<-as.factor(reco_iq$sex)
reco_iq$subjectID<-as.factor(reco_iq$subjectID)


plot_reco_fa_by_iq <- plot_tract_profiles(
  df = reco_iq,
  y = c("dti_fa"),
  tracts = NULL,
  group_col = "fsiq_low",
  group_pal = "cbb",
  save_figure = FALSE
)
plot_reco_fa_by_iq 

## Fit models recobundles (only CC segments, bilat CST)

###################### CC Forceps Major ######################
recoCCfmaj_iq_fit <- tractable_single_tract(
  df = reco_iq,
  tract = "CC_ForcepsMajor",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

recoCCfmaj_iq_summary <- summary(recoCCfmaj_iq_fit)
recoCCfmaj_iq_summary

####################### CC Mid ############################
recoCCmid_iq_fit <- tractable_single_tract(
  df = reco_iq,
  tract = "CCMid",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

recoCCmid_iq_summary <- summary(recoCCmid_iq_fit)
recoCCmid_iq_summary

#################### CC Forceps Minor ################
recoCCfmin_iq_fit <- tractable_single_tract(
  df = reco_iq,
  tract = "CC_ForcepsMinor",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto"
)

recoCCfmin_iq_summary <- summary(recoCCfmin_iq_fit)
recoCCfmin_iq_summary

##################### L CST ################
recoLCST_iq_fit <- tractable_single_tract(
  df = reco_iq,
  tract = "CST_L",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto",
  na_omit =TRUE
)

recoLCST_iq_summary <- summary(recoLCST_iq_fit)
recoLCST_iq_summary

################### R CST ######################
recoRCST_iq_fit <- tractable_single_tract(
  df = reco_iq,
  tract = "CST_R",
  target = "dti_fa",
  regressors = c("site", "sex", "fsiq_low"),
  node_group = "fsiq_low",
  k = "auto",
  na_omit =TRUE
)

recoRCST_iq_summary <- summary(recoRCST_iq_fit)
recoRCST_iq_summary

```

## SES Risk Score
```{r fit SRS}

RATh_srs_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Anterior Thalamic",
  target = "dti_fa",
  regressors = c("site", "srs_cumulative_high"),
  node_group = "srs_cumulative_high",
  k = "auto"
)

RATh_srs_summary <- summary(RATh_srs_fit)
RATh_srs_summary

LAF_srs_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Arcuate",
  target = "dti_fa",
  regressors = c("site", "srs_cumulative_high"),
  node_group = "srs_cumulative_high",
  k = "auto"
)

LAF_srs_summary <- summary(LAF_srs_fit)
LAF_srs_summary

```



# Now with Recobundles outputs
```{r load_data}
recobundles<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/Site-160_ELGAN/derivatives/afq_recobundles/tract_profiles.csv")



reco<-inner_join(recobundles, elgan, by= "subjectID") 



reco$sex<-as.factor(reco$sex)
reco$subjectID<-as.factor(reco$subjectID)
reco$bw_group<-as.factor(reco$bw_group)
reco$ga_group<-as.factor(reco$ga_group)

```

# Plot tract profiles - Recobundles
```{r plot_profiles_reco}
#plot by GA
plot_reco_ga <- plot_tract_profiles(
  df = reco,
  y = c("dti_fa"),
  tracts = c("CC_ForcepsMinor", "CC_ForcepsMajor", "CST_L", "CST_R", "IFOF_L", "IFOF_R"),
  group_col = "ga_group",
  save_figure = FALSE
)
plot_reco_ga

# Plot by BW
plot_reco_bw <- plot_tract_profiles(
  df = reco,
  y = c("dti_fa"),
  tracts = c("CST_L", "CST_R", "IFOF_L", "IFOF_R", "CC_ForcepsMinor", "CC_ForcepsMajor"),
  group_col = "bw_group",
  save_figure = FALSE
)
plot_reco_bw


```
# Fit GAMs by tract
## CC - FM
Make sure node group variable and subjectID are set as factors, else an error will occur
```{r cst_model_fit_reco}

ccfm_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CC_ForcepsMajor",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

ccfm_reco_summary <- summary(ccfm_reco_fit)
ccfm_reco_summary

ccfm_ga_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CC_ForcepsMajor",
  target = "dti_fa",
  regressors = "ga_group",
  node_group = "ga_group",
  k = "auto"
)

ccfm_ga_reco_summary <- summary(ccfm_ga_reco_fit)
ccfm_ga_reco_summary



```

## IFO
```{r ifo_model_fit_reco}
rifo_bw_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_R",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

rifo_bw_reco_summary <- summary(rifo_bw_reco_fit)
rifo_bw_reco_summary
# MARGINAL

lifo_bw_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_L",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

lifo_bw_reco_summary <- summary(lifo_bw_reco_fit)
lifo_bw_reco_summary



lifo_ga_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_L",
  target = "dti_fa",
  regressors = "ga_group",
  node_group = "ga_group",
  k = "auto"
)

lifo_ga_reco_summary <- summary(lifo_ga_reco_fit)
lifo_ga_reco_summary

rifo_ga_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_R",
  target = "dti_fa",
  regressors = "ga_group",
  node_group = "ga_group",
  k = "auto"
)

rifo_ga_reco_summary <- summary(rifo_ga_reco_fit)
rifo_ga_reco_summary

```

# CST Recobundles
```{r CST Recobundles}
rcst_bw_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CST_R",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

rcst_bw_reco_summary <- summary(rcst_bw_reco_fit)
rcst_bw_reco_summary



lcst_ga_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CST_L",
  target = "dti_fa",
  regressors = "ga_group",
  node_group = "ga_group",
  k = "auto"
)

lcst_ga_reco_summary <- summary(lcst_ga_reco_fit)
lcst_ga_reco_summary
##MARGINAL

rcst_ga_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CST_R",
  target = "dti_fa",
  regressors = "ga_group",
  node_group = "ga_group",
  k = "auto"
)

rcst_ga_reco_summary <- summary(rcst_ga_reco_fit)
rcst_ga_reco_summary


```