---
title: "Tractable Test"
output: html_notebook
---

Testing Tractable to run GAMs on pyAFQ tractometry outputs with Elgan3 UMMS data

# Load libraries
```{r setup}
library(tractable)
library(dplyr)
library(ggplot2)
```

# Load data - AFQ waypoints tracts

```{r load_data}
afqtracts<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/derivatives/afq/tract_profiles.csv")

demos<-read.table("/Volumes/LaCie/Projects/elgan_dti/data/participants.tsv", header=TRUE, sep="\t")

demos$ga_days<-as.numeric(demos$ga_days)

demos$bw<-as.numeric(demos$bw)

elgan<-demos[1:21,] %>%
        filter(dti_include != 0) 
      
# Calculate the median of 'bw', excluding NAs
median_bw <- median(elgan$bw, na.rm = TRUE)

# Create the 'bw_group' column
elgan$bw_group <- ifelse(is.na(elgan$bw), NA, ifelse(elgan$bw > median_bw, "High", "Low"))

# Optionally convert to factor
elgan$bw_group <- factor(elgan$bw_group, levels = c("Low", "High"))

# Calculate the median of 'ga_days', excluding NAs
median_ga <- median(elgan$ga_days, na.rm = TRUE)

# Create the 'ga_group' column
elgan$ga_group <- ifelse(elgan$ga_days > median_ga, "High", "Low")




afq<-inner_join(afqtracts, elgan, by= "subjectID") 


afq$sex<-as.factor(afq$sex)
afq$subjectID<-as.factor(afq$subjectID)
afq$bw_group<-as.factor(afq$bw_group)
afq$ga_group<-as.factor(afq$ga_group)

```

# Participants summary
```{r}
library(psych)



describe(elgan, na.rm= TRUE)



```

# Plot Profiles - AFQ waypoints tracts
```{r plot_profiles_afq}
plot_afq <- plot_tract_profiles(
  df = afq,
  y = c("dti_fa"),
  tracts = c("Left Corticospinal", "Right Corticospinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Callosum Superior Frontal", "Callosum Posterior Parietal"),
  group_col = "sex",
  save_figure = FALSE
)
plot_afq

# Now plot by ga median split
plot_ga_afq <- plot_tract_profiles(
  df = afq,
  y = c("dti_fa"),
  tracts = c("Left Corticospinal", "Right Corticospinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Callosum Superior Frontal", "Callosum Posterior Parietal"),
  group_col = "ga_group",
  save_figure = FALSE
)
plot_ga_afq


# Now plot by birthweight median split
plot_bw_afq <- plot_tract_profiles(
  df = afq,
  y = c("dti_fa"),
  tracts = c("Left Corticospinal", "Right Corticospinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Callosum Superior Frontal", "Callosum Posterior Parietal"),
  group_col = "bw_group",
  save_figure = FALSE
)
 plot_bw_afq

```
# Fit GAMs by tract - AFQ Waypoints Tracts
## CST
Make sure node group variable and subjectID are set as factors, else an error will occur
```{r cst_model_fit}


rcst_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Corticospinal",
  target = "dti_fa",
  regressors = c("ga_group"),
  node_group = "ga_group",
  k = "auto"
)

rcst_summary <- summary(rcst_fit)
rcst_summary



# Now testing by birthweight median split
rcst_bw_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Corticospinal",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

rcst_bw_summary <- summary(rcst_bw_fit)
rcst_bw_summary



lcst_bw_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Corticospinal",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

lcst_bw_summary <- summary(lcst_bw_fit)
lcst_bw_summary

```

## IFO
```{r ifo_model_fit}


rifo_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

rifo_summary <- summary(rifo_fit)
rifo_summary



lifo_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

lifo_summary <- summary(lifo_fit)
lifo_summary


rifo_fit <- tractable_single_tract(
  df = afq,
  tract = "Right Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

rifo_summary <- summary(rifo_fit)
rifo_summary


# Now testing by birthweight median split
lifo_bw_fit <- tractable_single_tract(
  df = afq,
  tract = "Left Inferior Fronto-occipital",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

lifo_bw_summary <- summary(lifo_bw_fit)
lifo_bw_summary

```

# Now with Recobundles outputs
```{r load_data}
recobundles<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/derivatives/afq_recobundlesRefine/tract_profiles.csv")



reco<-inner_join(recobundles, elgan, by= "subjectID") 



reco$sex<-as.factor(reco$sex)
reco$subjectID<-as.factor(reco$subjectID)
reco$bw_group<-as.factor(reco$bw_group)
reco$ga_group<-as.factor(reco$ga_group)

```

# Plot tract profiles - Recobundles
```{r plot_profiles_reco}
#plot by GA
plot_reco_ga <- plot_tract_profiles(
  df = reco,
  y = c("dti_fa"),
  tracts = c("CST_L", "CST_R", "IFOF_L", "IFOF_R", "CC_ForcepsMinor", "CC_ForcepsMajor"),
  group_col = "ga_group",
  save_figure = FALSE
)
plot_reco_ga

# Plot by BW
plot_reco_bw <- plot_tract_profiles(
  df = reco,
  y = c("dti_fa"),
  tracts = c("CST_L", "CST_R", "IFOF_L", "IFOF_R", "CC_ForcepsMinor", "CC_ForcepsMajor"),
  group_col = "bw_group",
  save_figure = FALSE
)
plot_reco_bw


```
# Fit GAMs by tract
## CC - FM
Make sure node group variable and subjectID are set as factors, else an error will occur
```{r cst_model_fit_reco}

ccfm_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CC_ForcepsMajor",
  target = "dti_fa",
  regressors = "bw_group",
  node_group = "bw_group",
  k = "auto"
)

ccfm_reco_summary <- summary(ccfm_reco_fit)
ccfm_reco_summary



lcst_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "CST_L",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

lcst_reco_summary <- summary(lcst_reco_fit)
lcst_reco_summary

```

## IFO
```{r ifo_model_fit_reco}
rifo_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_R",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

rifo_reco_summary <- summary(rifo_reco_fit)
rifo_reco_summary



lifo_reco_fit <- tractable_single_tract(
  df = reco,
  tract = "IFOF_L",
  target = "dti_fa",
  regressors = "sex",
  node_group = "sex",
  k = "auto"
)

lifo_reco_summary <- summary(lifo_reco_fit)
lifo_reco_summary

```