---
title: "Tractable Test"
output: html_notebook
---

Tractable GAMs on pyAFQ tractometry outputs with Elgan3 UMMS data

## Compile and summarize demographic data
```{r demographics}
library(tidyverse)
library(psych)

sublist<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/afq_include.csv")

demog<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/mergedcorrecteddata_cleaned_MP.csv") %>%
  select("sid", "bw", "sex", "female", "ivhx", "gadays", "plurality", "multip", "dx120_4_asd",	"dx120_5_cp", "epil", "iq85")

demog2<-read.csv("/Volumes/LaCie/Projects/elgan_dti/data/elgan_demog_data.csv") %>%
  select("sid", "develop", "AgeDecimalYRDIF", "FSIQ2", "srs15")
colnames(demog2)<-c("sid", "develop", "mri_age", "FSIQ2", "srs15")

tmp<-left_join(sublist, demog, by="sid")

subinfo<-left_join(tmp, demog2, by="sid")

# combine diagnosis variables

subinfo <- subinfo |>
  mutate(ndd = as.integer(
    (dx120_4_asd > 0 & !is.na(dx120_4_asd)) | 
    (dx120_5_cp  > 0 & !is.na(dx120_5_cp))  | 
    (epil        > 0 & !is.na(epil)) |
    (iq85        > 0 & !is.na(iq85))  
  ))

subinfo <- subinfo |>
  mutate(lowiq = as.integer(
    (FSIQ2 <70 & !is.na(FSIQ2)) 
  ))


## create median split variables

# Calculate the median of 'ga_days', excluding NAs
median_bw <- median(subinfo$bw, na.rm = TRUE)

# Create the 'bw_group' column
subinfo$bw_group <- ifelse(is.na(subinfo$bw), NA, ifelse(subinfo$bw > median_bw, "High", "Low"))

# Optionally convert to factor
subinfo$bw_group <- factor(subinfo$bw_group, levels = c("Low", "High"))

# Calculate the median of 'ga_days', excluding NAs
median_ga <- median(subinfo$gadays, na.rm = TRUE)

# Create the 'ga_group' column
subinfo$ga_group <- ifelse(subinfo$gadays > median_ga, "High", "Low")

# Create IQ split variable at 85
subinfo$IQunder85 <- ifelse(subinfo$FSIQ2 < 85, "Low", "Avg")


## describe data

subinfo %>% count(female)
subinfo %>% count(ndd)
subinfo %>% count(lowiq)
subinfo %>% count(ivhx)
subinfo %>% count(IQunder85)
subinfo %>% count(iq85) # coded from mergedandcorrected data sheet

describe(subinfo)

```

# Load data - AFQ waypoints tracts

```{r}

library(tidyverse)

# Define base path and site IDs
base_path <- "/Volumes/LaCie/Projects/elgan_dti/data"
sites <- c("site-120", "site-130", "site-140", "site-150", "site-160",
           "site-170", "site-220", "site-230", "site-310", "site-320", "site-330")

# Build file paths
tract_profile_paths <- file.path(base_path, sites, "derivatives", "afq", "tract_profiles.csv")

# Name the vector so site labels are preserved
names(tract_profile_paths) <- sites

# Vendor lookup
vendor_map <- c(
  "site-120" = "Siemens",
  "site-130" = "Siemens",
  "site-140" = "Siemens",      
  "site-150" = "Philips",
  "site-160" = "Philips",
  "site-170" = "Siemens",
  "site-220" = "Siemens",
  "site-230" = "Siemens",
  "site-310" = "GE",
  "site-320" = "GE",
  "site-330" = "Philips"
)

# Read and combine, adding 'site' and 'vendor' columns
tract_profiles_combined <- tract_profile_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site") |>
  mutate(vendor = vendor_map[site]) |>
  type_convert()

# Preview
glimpse(tract_profiles_combined)

# Add demographic data to tract profiles
elgan_afq_prob<-inner_join(tract_profiles_combined, subinfo, by = "subjectID")

# read in QSIprep QC data and select relevant columns
qc<-read.csv(file.path(base_path, "qsiprep_qc_combined.csv")) %>%
  mutate(
    subjectID = str_remove(subjectID, "^sub-"),
    sessionID = str_remove(sessionID, "^ses-")
  )

# add QC data to tract profiles
elgan_afq_prob<-inner_join(elgan_afq_prob, qc, by = "subjectID")

# Write compiled data to csv file
write.csv(elgan_afq_prob,"/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_all.csv", row.names=FALSE)

# Load database for analysis
elgan_afq_prob <- read.csv("/Volumes/LaCie/Projects/elgan_dti/data/ELGAN_afq_prob_all.csv") %>%
    mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, IQunder85, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))

elgan_afq_prob <- elgan_afq_prob %>%
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, IQunder85, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))


```




## Exclude bad tracts
Filter out tracts that were deemed 'poor' based on visual QC
This is totally subjective so consider alternative more objective methods of QC by including parameters from QSIprep/eddy QC outputs
```{r exclude tracts}

# Read the inclusion spreadsheet
tract_include_paths <- file.path(base_path, sites, "derivatives", "afq_include_by_tract.csv")

# Read and combine, adding 'site' and 'vendor' columns
tract_include_combined <- tract_include_paths |>
  map(\(path) {
    if (file.exists(path)) {
      read_csv(path, show_col_types = FALSE, col_types = cols(.default = "c"))
    } else {
      warning(paste("File not found:", path))
      NULL
    }
  }) |>
  compact() |>
  list_rbind(names_to = "site")

tract_include_combined <- tract_include_combined |>
  mutate(across(c(subjectID, sessionID), as.factor)) 

# Join and filter out excluded subject-tract pairs
elgan_afq_prob_cleantracts <- elgan_afq_prob |>
  left_join(
    tract_include_combined |> select(subjectID, sessionID, tractID, include_tract_prob),
    by = c("subjectID", "sessionID", "tractID")
  ) |>
  filter(include_tract_prob == 1) |>
  select(-include_tract_prob)

elgan_afq_prob_cleantracts <- elgan_afq_prob_cleantracts |>
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, IQunder85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))

```


# Plot Profiles 

## Compare tract profiles by vendor
```{r fa by vendor}
library(tractable)

plot_fa_by_vendor_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "vendor",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_vendor_clean

cc_sup_frontal_fa_by_vendor <- tractable_single_tract(
    df         = elgan_afq_prob_cleantracts,
    tract      = "Callosum Superior Frontal",
    target     = "dti_fa",
    regressors = c("mri_age", "female", "vendor"),
    node_group = "vendor"
)

summary(cc_sup_frontal_fa_by_vendor)


cc_post_parietal_fa_by_vendor <- tractable_single_tract(
    df         = elgan_afq_prob_cleantracts,
    tract      = "Callosum Posterior Parietal",
    target     = "dti_fa",
    regressors = c("mri_age", "female", "vendor"),
    node_group = "vendor"
)

summary(cc_post_parietal_fa_by_vendor)



plot_fa_by_site <- plot_tract_profiles(
  df = elgan_afq_prob,
  y = c("dti_fa"),
  tracts = c("Callosum Orbital", "Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "site",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_site


```
### What underlies the vendor differences? 
Check QC and acquisition parameter differences between vendors using ANOVA

```{r}
## reduce dataframe to relevant columns with 1 row per subject
df_qc<- elgan_afq_prob %>% 
          select("subjectID", "vendor", "site", 31:89) %>%
          distinct()

write.csv(df_qc, "/Volumes/LaCie/Projects/elgan_dti/data/qsiprep_qc_combined_vendor_site.csv", row.names=FALSE)
      
# Run ANOVA by Vendor

summary(aov(CNR0_mean ~ vendor, data=df_qc))

## post-hoc pairwise tests
TukeyHSD(aov(CNR0_mean ~ vendor, data=df_qc))

plot(TukeyHSD(aov(CNR0_mean ~ vendor, data=df_qc)))

summary(aov(CNR1_mean ~ vendor, data=df_qc))

## post-hoc pairwise tests
TukeyHSD(aov(CNR1_mean ~ vendor, data=df_qc))

summary(aov(mean_fd ~ vendor, data=df_qc))

summary(aov(mean_fd ~ vendor, data=df_qc))

# Run ANOVA by Site
summary(aov(CNR0_mean ~ site, data=df_qc))

## post hoc tests
TukeyHSD(aov(CNR0_mean ~ site, data=df_qc))


summary(aov(CNR1_mean ~ site, data=df_qc))

summary(aov(mean_fd ~ site, data=df_qc))






```


## Compare tract profiles by sex
```{r plot by sex}
library(tractable)

plot_fa_by_sex <- plot_tract_profiles(
  df = elgan_afq_prob,
  y = c("dti_fa"),
  tracts = c("Callosum Orbital", "Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "female",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_sex

plot_fa_by_sex_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "female",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_sex_clean


cc_post_parietal_fa_by_sex <- tractable_single_tract(
    df         = elgan_afq_prob_cleantracts,
    tract      = "Left Cingulum Cingulate",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female"),
    node_group = "female"
)

summary(cc_post_parietal_fa_by_sex)


```

## Plot Profiles by Birthweight
```{r plot by bw}

plot_fa_by_bw <- plot_tract_profiles(
  df = elgan_afq_prob,
  y = c("dti_fa"),
  tracts = c("Callosum Orbital", "Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "bw_group",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_bw

plot_fa_by_bw_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "bw_group",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_bw_clean



# test FA by birthweight 
left_cingulum_fa_by_bw <- tractable_single_tract(
    df         = elgan_afq_prob_cleantracts,
    tract      = "Left Cingulum Cingulate",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female", "bw_group"),
    node_group = "bw_group"
)

summary(left_cingulum_fa_by_bw)

```


## Plot Profiles by Gestational Age
```{r plot by ga}

plot_fa_by_ga <- plot_tract_profiles(
  df = elgan_afq_prob,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "ga_group",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_ga

# test FA by GA all tracts 
cc_sup_parietal_fa_by_ga <- tractable_single_tract(
    df         = elgan_afq_prob,
    tract      = "Callosum Superior Parietal",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female", "ga_group"),
    node_group = "ga_group"
)
summary(cc_sup_parietal_fa_by_ga)

## add QC covariates - CNR
cc_sup_parietal_fa_by_ga_cnr <- tractable_single_tract(
    df         = elgan_afq_prob,
    tract      = "Callosum Superior Parietal",
    target     = "dti_fa",
    regressors = c("ga_group", "CNR0_mean"),
    node_group = "ga_group"
)
summary(cc_sup_parietal_fa_by_ga_cnr)

## use data with selected tracts removed based on visual QC
plot_fa_by_ga_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "ga_group",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_ga_clean

# test FA by GA cleantracts
cc_sup_parietal_fa_by_ga <- tractable_single_tract(
    df         = elgan_afq_prob_cleantracts,
    tract      = "Callosum Superior Parietal",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female", "ga_group"),
    node_group = "ga_group"
)

summary(cc_sup_parietal_fa_by_ga)


```

## Plot Profiles by Intraventricular Hemm.
```{r plot by ivh}

plot_fa_by_ivh <- plot_tract_profiles(
  df = elgan_afq_prob,
  y = c("dti_fa"),
  tracts = c("Callosum Orbital", "Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "ivhx",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_ivh

plot_fa_by_ivh_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "ivhx",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_ivh_clean

supfrontCC_fa_by_ga <- tractable_single_tract(
    df         = elgan_afq_prob,
    tract      = "Callosum Superior Frontal",
    target     = "dti_fa",
    regressors = c("mri_age", "site", "ga_group"),
    node_group = "ga_group",
    k          = "auto"
)

summary(supfrontCC_fa_by_ga)


```


## Plot Profiles by IQ <>85
```{r plot by iq}
#subset dataframe with IQ data
elgan_afq_prob_iq <- elgan_afq_prob_cleantracts %>% 
                        filter(!is.na(iq85)) 
elgan_afq_prob_iq <- elgan_afq_prob_iq |>
  mutate(across(c(subjectID, sex, ndd, lowiq, female, site, vendor, ivhx, iq85, ga_group, bw_group), as.factor)) |>
  mutate(across(c(dti_fa, dti_md), as.numeric))                        




plot_fa_by_iq_clean <- plot_tract_profiles(
  df = elgan_afq_prob_iq,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "iq85",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_iq_clean



# test group dif in CC post-parietal
cc_sup_parietal_fa_by_IQ <- tractable_single_tract(
    df         = elgan_afq_prob_iq,
    tract      = "Callosum Superior Parietal",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female", "iq85"),
    node_group = "iq85"
)

summary(cc_sup_parietal_fa_by_IQ)


# add random effect of site
cc_sup_parietal_fa_by_IQ_REsite <- tractable_single_tract(
    df         = elgan_afq_prob_iq,
    tract      = "Callosum Posterior Parietal",
    target     = "dti_fa",
    regressors = c("mri_age", "vendor", "female", "iq85",
                   "s(site, bs = 're')"),
    node_group = "iq85"
)

summary(cc_post_parietal_fa_by_IQ_REsite)


# loop GAMM over all tracts
library(purrr)

tracts <- c(
  "Callosum Anterior Frontal", "Callosum Superior Frontal",
  "Callosum Motor", "Callosum Superior Parietal",
  "Callosum Posterior Parietal", "Callosum Occipital",
  "Left Corticospinal", "Right Corticospinal",
  "Left Cingulum Cingulate", "Right Cingulum Cingulate",
  "Left Anterior Thalamic", "Right Anterior Thalamic",
  "Left Inferior Longitudinal", "Right Inferior Longitudinal",
  "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital",
  "Left Superior Longitudinal", "Right Superior Longitudinal",
  "Left Arcuate", "Right Arcuate"
)

fa_iq_models <- tracts |>
  set_names() |>
  map(\(tract) {
    message("Fitting: ", tract)
    tractable_single_tract(
      df         = elgan_afq_prob_iq,
      tract      = tract,
      target     = "dti_fa",
      regressors = c("mri_age", "vendor", "female", "iq85"),
      node_group = "iq85"
    )
  })
#To get the summary for any tract: summary(fa_iq_models[["Left Arcuate"]])

summary(fa_iq_models[["Callosum Superior Parietal"]])



```

## Plot Profiles by NDD
```{r plot by ndd}
#subset dataframe with ndd data
elgan_afq_prob_ndd <- elgan_afq_prob %>% 
                        filter(!is.na(ndd))


plot_fa_by_ndd_clean <- plot_tract_profiles(
  df = elgan_afq_prob_cleantracts,
  y = c("dti_fa"),
  tracts = c("Callosum Anterior Frontal", "Callosum Superior Frontal", "Callosum Motor", "Callosum Superior Parietal", "Callosum Posterior Parietal", "Callosum Occipital", "Left Corticospinal", "Right Corticospinal", "Left Cingulum Cingulate", "Right Cingulum Cingulate","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Inferior Fronto-occipital", "Right Inferior Fronto-occipital", "Left Superior Longitudinal", "Right Superior Longitudinal", "Left Arcuate", "Right Arcuate"),
  group_col = "ndd",
  group_pal = "cbb",
  save_figure = FALSE)
plot_fa_by_ndd_clean


```


### FDR correction for FSIQ models
```{r FDR corr}
tracts<-c("CC Anterior Frontal", "CC Motor", "CC Occipital", "CC Orbital", "CC Posterior Parietal", "CC Superior Frontal", "CC Superior Parietal","Left Anterior Thalamic", "Right Anterior Thalamic", "Left Arcuate", "Right Arcuate", "Left Cingulum", "Right Cingulum", "Left Corticospinal", "Right Corticospinal", "Left Inferior Fronto-Occipital", "Right Inferior Fronto-Occipital", "Left Inferior Longitudinal", "Right Inferior Longitudinal", "Left Superior Longitudinal", "Right Superior Longitudinal")

fitcoef<-c(CCant_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.coeff"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LATh_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RATh_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LAF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RAF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LCing_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RCing_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LCST_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RCST_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LILF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          RILF_iq_summary[["p.coeff"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.coeff"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.coeff"]][["fsiq_low1"]])

tvals<-c(CCant_iq_summary[["p.t"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.t"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.t"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.t"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.t"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.t"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.t"]][["fsiq_low1"]],
          LATh_iq_summary[["p.t"]][["fsiq_low1"]],
          RATh_iq_summary[["p.t"]][["fsiq_low1"]],
          LAF_iq_summary[["p.t"]][["fsiq_low1"]],
          RAF_iq_summary[["p.t"]][["fsiq_low1"]],
          LCing_iq_summary[["p.t"]][["fsiq_low1"]],
          RCing_iq_summary[["p.t"]][["fsiq_low1"]],
          LCST_iq_summary[["p.t"]][["fsiq_low1"]],
          RCST_iq_summary[["p.t"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.t"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.t"]][["fsiq_low1"]],
          LILF_iq_summary[["p.t"]][["fsiq_low1"]],
          RILF_iq_summary[["p.t"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.t"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.t"]][["fsiq_low1"]])

pvals<-c( CCant_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCmot_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCocc_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCorb_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCpostp_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCsupf_iq_summary[["p.pv"]][["fsiq_low1"]],
          CCsuppar_iq_summary[["p.pv"]][["fsiq_low1"]],
          LATh_iq_summary[["p.pv"]][["fsiq_low1"]],
          RATh_iq_summary[["p.pv"]][["fsiq_low1"]],
          LAF_iq_summary[["p.pv"]][["fsiq_low1"]],
          RAF_iq_summary[["p.pv"]][["fsiq_low1"]],
          LCing_iq_summary[["p.pv"]][["fsiq_low1"]],
          RCing_iq_summary[["p.pv"]][["fsiq_low1"]],
          LCST_iq_summary[["p.pv"]][["fsiq_low1"]],
          RCST_iq_summary[["p.pv"]][["fsiq_low1"]],
          LIFO_iq_summary[["p.pv"]][["fsiq_low1"]],
          RIFO_iq_summary[["p.pv"]][["fsiq_low1"]],
          LILF_iq_summary[["p.pv"]][["fsiq_low1"]],
          RILF_iq_summary[["p.pv"]][["fsiq_low1"]],
          LSLF_iq_summary[["p.pv"]][["fsiq_low1"]], 
          RSLF_iq_summary[["p.pv"]][["fsiq_low1"]])

pfdr<-p.adjust(pvals, method = "fdr", n=length(pvals))

results_iq<-data_frame(tracts, fitcoef, tvals, pvals, pfdr)

write.csv(results_iq, "/Users/meaghan/Library/CloudStorage/OneDrive-UMassChanMedicalSchool/ELGAN/ELGAN_Tractometry/abstracts/ohbm_results.csv")


```

